\section*{References}

\begin{thebibliography}{1}
\bibitem{CMS}
The CMS Collaboration 2008 The CMS experiment at the CERN LHC {\it JINST {\bf 3} S08004}

\bibitem{WLCG}
Knoblock J {\it et al.} 2005 LHC Computing Grid Technical Design Report {\it CERN-LHCC-2005-024}

\bibitem{OliOps}
 Gutsche O {\it et.al.} CMS Computing Operations during Run 1, {\it submitted to CHEP 2013}

\bibitem{PhEDEx}
  Egeland R, Wildish T and Metson S 2008 Data transfer infrastructure for CMS data taking,  {\it XII Advanced Computing and Analysis Techniques in Physics Research (Erice, Italy: Proceedings of Science)}

\bibitem{DBS}
Giffels M Data Bookkeeping Service 3 - Providing event metadata in CMS, {\it submitted to CHEP 2013}

\bibitem{DAS}
Kuznetsov V, Evans D and Metson S The CMS Data Aggregation System
{\it doi:10.1016/j.procs.2010.04.172}

\bibitem{CTDR}
The CMS Collaboration 2005 The Computing Project Technical Design Report CERN-LHCC-2005-023

\bibitem{phedexweb}
R Egeland {\it et.al.} 2012  The PhEDEx next-gen website {\it J. Phys. Conf. Ser.} {\bf 396} 032117

\bibitem{phedexdatasvc}
R Egeland {\it et al.} 2010  PhEDEx Data Service {\it J. Phys.: Conf. Ser.} {\bf 219} 062010

\bibitem{poe}
The Perl Object Environment (POE)  {\it http://poe.perl.org/}

\bibitem{lifecycle}
T Wildish {\it et al.} Integration and validation testing for PhEDEx, DBS and DAS with the PhEDEx LifeCycle agent,
{\it submitted to CHEP 2013}

\bibitem{phedexlatency}
T Chwalek {\it et al.} 2012  No file left behind - monitoring transfer latencies in PhEDEx {\it J. Phys.: Conf. Ser.} {\bf 396} 032089

\bibitem{phedexframework}
A Sanchez-Hernandez {\it et al.} 2012 From toolkit to framework - the past and future evolution of PhEDEx {\it J. Phys.: Conf. Ser.} {\bf 396} 032118

\bibitem{storagemon}
C-H Huang {\it et al.}  2012 Data Storage Accounting and Verification at LHC experiments  {\it J. Phys.: Conf. Ser.} {\bf 396} 032090 

\bibitem{phedexrequests}
C-H Huang Request for All - Generalized Request Framework for PhEDEx,
{\it submitted to CHEP 2013}

\bibitem{DBS2} Afaq A {\it et al.} 2008 The CMS Dataset Bookkeeping Service
{\it J. Phys. Conf. Ser.} 
{\bf 119} 072001

\bibitem{CMSDBs} Pfeiffer A {\it et al.} 2012 CMS experience with online and offline databases 
{\it J.Phys.Conf.Ser.} 
{\bf 396}

\bibitem{REST} Fielding R T 2000 Architectural Styles and the Design of Network-based Software Architectures, Dissertation, 
{\it University of California, Irvine} 
ISBN: 0-599-87118-0

\bibitem{MongoDB}
http://www.mongodb.org/

\bibitem{MVC} Model-view-controller architecture {\it http://en.wikipedia.org/wiki/Model-view-controller}

\bibitem{DASKWS} Zemleris V and Kuznetsov V 
Keyword Search over Data Service Integration for Accurate Results,
{\it submitted to CHEP 2013}

\bibitem{victor} F H Barreiro Megino {\it et al.} 2012 Implementing data placement strategies for the CMS experiment based on a popularity model 
{\it J. Phys.: Conf. Ser.} {\bf 396} 032047

\end{thebibliography}
