PhEDEx \cite{PhEDEx}, DBS \cite{DBS} and DAS \cite{DAS} are the core components of the CMS Data 
Management system \cite{CMSDMS}. PhEDEx is responsible for moving data around the CMS computing 
sites, DBS is responsible for maintaining knowledge of the physics content of the data, and DAS is 
a portal that provides physicists with integrated access to PhEDEx, DBS, and other services.

The development model for these services is highly decoupled. Each is developed by a separate team 
of people, and each provides a web-based data service for access to information. Ensuring 
stability and consistency of these interfaces has, until recently, been poorly managed. We have 
relied on stability of the underlying services and coordination between developers to ensure that 
successive releases of the software are coherent and correct.

In this paper we describe part of the solution to this problem. The {\it LifeCycle agent}, written 
originally for scale-testing of PhEDEx, has been extended to provide cross-component integrated 
testing in a flexible and powerful manner. Components can be tested individually or together in 
different ways for verification, debugging, or scale and performance testing. The LifeCycle agent 
itself scales well, and is easily adapted to new requirements (e.g. testing of new APIs from the 
services). It can inject data into the component systems, retrieve it, manipulate it, and compare 
it with expectations to detect errors. It can also test expected error conditions for correct 
behaviour (e.g. access with an unauthorised certificate).
